Mixed effect tweedie model in TMB

### 2019-04-14 analysis/tmb-sensor-explore/2-fit-temperature.Rmd

cv_loglik <- c()
for (i in seq_len(nrow(cv_args))) {
  cv_loglik[[i]] <- c(sdmTMB_cv_batch[[i]]$sum_loglik)
}
cv_args2 <- cv_args
cv_args2$formula <- as.character(cv_args$formula)
cv_args2$time_varying <- as.character(cv_args$time_varying)
cv_args2$cv_loglik <- cv_loglik
glimpse(cv_args2)
cv_args_tv <- as.data.frame(cv_args2) 
write.csv(cv_args_tv, file="cv-all-time-varying.csv")
saveRDS(sdmTMB_cv_batch, file = "cv-all-time-varying.rds")
# readRDS(file = "sdmTMB_cv_nontv.rds")
```

>>>>

cv_loglik <- c()
for (i in seq_len(nrow(cv_args))) {
  cv_loglik[[i]] <- c(sdmTMB_cv_batch[[i]]$sum_loglik)
}
cv_args2 <- cv_args
cv_args2$formula <- as.character(cv_args$formula)
cv_args2$time_varying <- as.character(cv_args$time_varying)
cv_args2$cv_loglik <- cv_loglik
glimpse(cv_args2)
cv_args_tv <- as.data.frame(cv_args2) 
write.csv(cv_args_tv, file="cv-all-time-varying.csv")

saveRDS(sdmTMB_cv_batch, file = "cv-all-time-varying.rds")
# readRDS(file = "sdmTMB_cv_nontv.rds")
```
